---
title: "Shreya Kolalapudi"
author: "Shreya Kolalapudi"
date: "30/07/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Invoke all your packages here()
# library(blah blah)

```

## Introduction

> Introduce yourself briefly. Describe briefly what you are going to
> show here.

## Graph 1

We had to recrete the graph from the website, so I extracted the data and then analizied and understood the data so that I could represent it in the graph format.

```{r read-1}
my_data_1 <- read_csv(".data/something.csv")
glimpse(my_data_1)

```

Describe briefly what graph you are going to plot

```{r plot-1}
my_data_1 %>% ggplot....

```

Brief concluding remarks. What does the graph show? What geometric aesthetics did you use, for example?

## Graph 2

Brief introduction of your chosen data set Describe the interesting
columns and what they mean

```{r read-2}
my_data_2 <- read_csv(".Data/something.csv")
glimpse(my_data_2)

```

Describe briefly what graph you are going to plot

```{r plot-2}
my_data_2 %>% ggplot....

```

## Graph 3

Brief introduction of your chosen data set Describe the interesting
columns and what they mean

```{r read-3}
my_data_3 <- .....
glimpse(my_data_3)
```

Describe briefly what graph you are going to plot

```{r plot-3}


```

## My Course Reflection

This course was about.....

What I learnt....

How it will help my practice as an aspiring artist and designer....

Arvind is a horrible teacher and simply does not get what we need. Boomers should be allowed to teach any more in Srishti.

Etc.

Jai Hind.
